PyBOP: A Python package for battery model optimisation and parameterisation

### 2024-12-20 papers/joss/paper.preprint.tex
Updates figures, /joss directory -> /papers

@@

\affil[1]{Department of Engineering Science, University of Oxford,
Oxford, UK%
  }
\affil[2]{The Faraday Institution, Harwell Campus, Didcot, UK%
  }
\affil[3]{Research Software Engineering Group, University of Oxford,
Oxford, UK%
  }
\affil[4]{Quansight Labs%
  }
\affil[5]{Mathematics Institute, University of Warwick, Coventry, UK%
  }
\affil[$\mathparagraph$]{Corresponding author: %
   %
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\date{04 December 2024}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/sim-landscape.png}
\caption{The fitted synthetic dataset (left) and cost landscape (right)
for an example time-series battery model parameterisation using a
root-mean-squared error cost function.
\label{fig:inference-time-landscape}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/impedance.png}
\caption{The data and model fit (left) and cost landscape (right) for a
frequency-domain impedance parameterisation with a root-mean-squared
error cost function, at 5\% SOC. \label{fig:impedance-landscape}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/converge.png}
\caption{Optimiser convergence using various cost (left) and likelihood
(right) functions and the L-BFGS-B algorithm.
\label{fig:convergence-min-max}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/optimisers_parameters.png}
\caption{Convergence in parameter values for several optimisation
algorithms provided by \texttt{PyBOP}. \label{fig:optimiser-inference1}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/contour_subplot.png}
\caption{Cost landscape contour plot with corresponding optimisation
traces, for several optimisers. \label{fig:optimiser-inference2}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/posteriors.png}
\caption{Posterior distributions of model parameters alongside
identified noise on the observations. Shaded area denotes the 95th
percentile credible interval for each parameter. \label{fig:posteriors}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/design.png}
\caption{Gravimetric energy density cost landscape alongside the initial
and optimised voltage profiles, for a fixed 1C discharge set from the
initial design. \label{fig:design_gravimetric}}
\end{figure}

>>>>

\usepackage[a4paper, total={6in, 8in}]{geometry}

@@

\affil[1]{Department of Engineering Science, University of Oxford,
Oxford, UK%
  }
\affil[2]{The Faraday Institution, Harwell Campus, Didcot, UK%
  }
\affil[3]{Research Software Engineering Group, University of Oxford,
Oxford, UK%
  }
\affil[4]{Quansight Labs%
  }
\affil[5]{Mathematics Institute, University of Warwick, Coventry, UK%
  }
\affil[$\mathparagraph$]{Corresponding author: %
   %
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\date{19 December 2024}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/sim-landscape.pdf}
\caption{The synthetic fitting dataset (left) and cost landscape (right)
for an example time-series battery model parameterisation using a
root-mean-squared error cost function.
\label{fig:inference-time-landscape}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/impedance.pdf}
\caption{The data and model fit (left) and cost landscape (right) for a
frequency-domain impedance parameterisation with a root-mean-squared
error cost function, at 5\% SOC. \label{fig:impedance-landscape}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/converge.pdf}
\caption{Optimiser convergence using various cost (left) and likelihood
(right) functions and the L-BFGS-B algorithm.
\label{fig:convergence-min-max}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/optimisers_parameters.pdf}
\caption{Convergence in parameter values for several optimisation
algorithms provided by \texttt{PyBOP}. \label{fig:optimiser-inference1}}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/contour_subplot.pdf}
\caption{Cost landscape contour plot with corresponding optimisation
traces, for several optimisers. \label{fig:optimiser-inference2}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/posteriors.pdf}
\caption{Posterior distributions of model parameters alongside
identified noise on the observations. Shaded area denotes the 95th
percentile credible interval for each parameter. \label{fig:posteriors}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{figures/joss/design.pdf}
\caption{Gravimetric energy density cost landscape alongside the initial
and optimised voltage profiles, for a fixed 1C discharge set from the
initial design. \label{fig:design_gravimetric}}
\end{figure}
